DATA 607 Project 2

### 2018-10-07 DATA607/Project_2.Rmd
More work on Project 2

---
title: "DATA 607 Project 2"
author: "Mike Silva"
date: "October 1, 2018"
output:
  html_document:
    theme: yeti
    highlight: tango
    toc: true
    toc_depth: 4
    toc_float: true
---

@@

```{r initialize, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(stringr)
library(kableExtra)

#output: 
#  rmdformats::readthedown:
#    highlight: kate
```

@@

##### Table 2. ACS Data Check
```{r acs_sanity_check_1, echo=FALSE}
acs_df %>%
  select(Workers, Earnings, Concentration) %>%
  summarise_all(funs(min=min, median=median, mean = mean, max=max)) %>%
  gather(stat, val) %>%
  separate(stat, into = c("Variable", "stat"), "_") %>%
  spread(stat, val) %>%
  select(Variable, min, mean, median, max) %>%
  kable() %>%
  kable_styling("striped")
```

@@

##### Table 3. ACS Data After Cleanup
```{r acs_sanity_check_2, echo=FALSE}
acs_df %>%
  select(Workers, Earnings, Concentration) %>%
  summarise_all(funs(min=min, median=median, mean = mean, max=max)) %>%
  gather(stat, val) %>%
  separate(stat, into = c("Variable", "stat"), "_") %>%
  spread(stat, val) %>%
  select(Variable, min, mean, median, max) %>%
  kable() %>%
  kable_styling("striped")
```

@@

```{r acs_viz, echo=FALSE}
library(ggplot2)
ratio_line <- median(acs_df$Ratio)

@@

##### Table 4. ACS Average Summary Statistics
```{r acs_average_by_occupation_summary, echo=FALSE}
acs_avg_df %>%
  select(Ratio, Concentration, N) %>%
  summarise_all(funs(min=min, median=median, mean = mean, max=max)) %>%
  gather(stat, val) %>%
  separate(stat, into = c("Variable", "stat"), "_") %>%
  spread(stat, val) %>%
  select(Variable, min, mean, median, max) %>%
  kable() %>%
  kable_styling("striped")
```

@@

##### Table 5. Top 5 Occupations with Income Inequality
```{r acs_highest_inequity, echo=FALSE}
acs_avg_df %>%
  arrange(Ratio) %>%
  top_n(5, -Ratio) %>%
  kable() %>%
  kable_styling("striped")
```

@@

##### Table 6. Top 5 Occupations with Lowest Income Inequality
```{r acs_lowest_inequity, echo=FALSE}
acs_avg_df %>%
  arrange(-Ratio) %>%
  top_n(5, Ratio) %>%
  kable() %>%
  kable_styling("striped")
```

@@

```{r acs_scatter_plot, echo=FALSE}
ggplot(acs_df, aes(Concentration, Ratio, alpha=0.0001)) + geom_point() + guides(alpha = "none")
```

@@

##### Table 9. Top 5 Migrant Destinations by Year
```{r top_recipient_table, echo=FALSE}
top_destinations %>%
  select(-Migrants) %>%
  spread(Year, Country) %>%
  arrange(Rank) %>%
  kable() %>%
  kable_styling("striped")
```

@@

##### Table 10. Countries the United States Immigrants Come From
```{r us_table, echo=FALSE}
rankings_df %>%
  select(-Migrants) %>%
  spread(Year, Country) %>%
  arrange(Rank) %>%
  kable() %>%
  kable_styling("striped")
```

@@

```{r, echo=FALSE}
arrest_df %>%
  filter(Type == "Total") %>%
  ggplot(aes(Year, Arrests, group=County)) + geom_line()
```

@@

```{r, echo=FALSE}
arrest_df %>%
  filter(Type == "Total") %>%
  ggplot(aes(Year, Change, group=County)) + geom_line() + geom_hline(aes(yintercept=0, color="red")) + guides(color=FALSE)
```

@@

```{r}
arrest_df %>%
  group_by(Year) %>%
  filter(Type == "Total") %>%
  select(Arrests, Change) %>%
  summarise_all(funs(min=min, median=median, mean = mean, max=max)) %>%
  gather(stat, val, -Year)  %>%
  separate(stat, into = c("Variable", "stat"), "_") %>%
  spread(stat, val) %>%
  select(Variable, Year, min, mean, median, max) %>%
  arrange(Variable, Year) %>%
  kable() %>%
  kable_styling("striped")

>>>>

---
title: "DATA 607 Project 2"
author: "Mike Silva"
date: "October 1, 2018"
output: 
  rmdformats::readthedown:
    highlight: kate
---

@@

```{r initialize, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(kableExtra)
```

@@

##### Table 2. ACS Data Check
```{r acs_sanity_check_1, echo=FALSE}
acs_df %>%
  select(Workers, Earnings, Concentration) %>%
  summarise_all(funs(min=min, median=median, mean = mean, max=max)) %>%
  gather(stat, val) %>%
  separate(stat, into = c("Variable", "stat"), "_") %>%
  spread(stat, val) %>%
  select(Variable, min, mean, median, max) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"))
```

@@

##### Table 3. ACS Data After Cleanup
```{r acs_sanity_check_2, echo=FALSE}
acs_df %>%
  select(Workers, Earnings, Concentration) %>%
  summarise_all(funs(min=min, median=median, mean = mean, max=max)) %>%
  gather(stat, val) %>%
  separate(stat, into = c("Variable", "stat"), "_") %>%
  spread(stat, val) %>%
  select(Variable, min, mean, median, max) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive")) %>%
  scroll_box(width = "100%", height = "200px")
```

@@

##### Figure 1. Earning Ratio Density Plot (Median Verticle Line in Red)
```{r acs_viz, echo=FALSE}
ratio_line <- median(acs_df$Ratio)

@@

##### Table 4. ACS Average Summary Statistics
```{r acs_average_by_occupation_summary, echo=FALSE}
acs_avg_df %>%
  select(Ratio, Concentration, N) %>%
  summarise_all(funs(min=min, median=median, mean = mean, max=max)) %>%
  gather(stat, val) %>%
  separate(stat, into = c("Variable", "stat"), "_") %>%
  spread(stat, val) %>%
  select(Variable, min, mean, median, max) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"))
```

@@

##### Table 5. Top 5 Occupations with Income Inequality
```{r acs_highest_inequity, echo=FALSE}
acs_avg_df %>%
  arrange(Ratio) %>%
  top_n(5, -Ratio) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"))
```

@@

##### Table 6. Top 5 Occupations with Lowest Income Inequality
```{r acs_lowest_inequity, echo=FALSE}
acs_avg_df %>%
  arrange(-Ratio) %>%
  top_n(5, Ratio) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"))
```

@@

##### Figure 2. Concentration and Earning Ratio Scatter Plot
```{r acs_scatter_plot, echo=FALSE}
ggplot(acs_df, aes(Concentration, Ratio, alpha=0.0001)) + geom_point() + guides(alpha = "none")
```

@@

##### Table 9. Top 5 Migrant Destinations by Year
```{r top_recipient_table, echo=FALSE}
top_destinations %>%
  select(-Migrants) %>%
  spread(Year, Country) %>%
  arrange(Rank) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"))
```

@@

##### Table 10. Countries the United States Immigrants Come From
```{r us_table, echo=FALSE}
rankings_df %>%
  select(-Migrants) %>%
  spread(Year, Country) %>%
  arrange(Rank) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive"))
```

@@

##### Figure 3. Total Adult Arrests by County and Year
```{r, echo=FALSE}
arrest_df %>%
  filter(Type == "Total") %>%
  ggplot(aes(Year, Arrests, group=County)) + geom_line()
```

@@

##### Figure 4. Percentage Change from 1970 Level (No Change in Red)
```{r, echo=FALSE}
arrest_df %>%
  filter(Type == "Total") %>%
  ggplot(aes(Year, Change, group=County)) + geom_line() + geom_hline(aes(yintercept=0, color="red")) + guides(color=FALSE)
```

@@

```{r}
arrest_df %>%
  group_by(Year) %>%
  filter(Type == "Total") %>%
  select(Arrests, Change) %>%
  summarise_all(funs(min=min, median=median, mean = mean, max=max)) %>%
  gather(stat, val, -Year)  %>%
  separate(stat, into = c("Variable", "stat"), "_") %>%
  spread(stat, val) %>%
  select(Variable, Year, min, mean, median, max) %>%
  arrange(Variable, Year) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive")) %>%
  scroll_box(width = "100%", height = "200px")
